Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-12-10 ms.qmd
Clarity on writing

Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change. Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change. This is because the acute and acclimation responses of wild ectotherms are expected to be lower in warmer environments.

>>>>

Understanding how the acclimation capacity and the opportunity for selection will change across populations and species is important for predicting the impacts of climate change. Here, we show that the opportunity for selection is expected to decrease for wild ectotherms under climate change, but particularly so for terrestrial ectotherms. Decreases in variance are larger than the expected benefits from acclimation.
